CMPSubset

### 2021-06-25 CMPSubset.Rmd
continued analyses on CMP and msAggr

```{r setup}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/")
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
# library(clustree)
```
store session info
```{r}
sink("CMP-v1.20210616.txt")
sessionInfo()
sink()
```

@@

```{r}
all.genes <- rownames(seurat.object)
seurat.object <- ScaleData(seurat.object, features = all.genes, vars.to.regress = c("nFeature_RNA", "nCount_RNA"))
```

@@

```{r}
DimPlot(seurat.object, reduction = "pca")
VizDimLoadings(seurat.object, dims = 1:6, nfeatures = 10, reduction = "pca", ncol = 3)

@@

@@

## Add cluster IDs from Seurat v1

do numbers make sense?

```{r}
nrow(seurat.object@meta.data[seurat.object@meta.data$clust.ID == 10,])
nrow(seurat.object@meta.data[seurat.object@meta.data$clust.ID == 11,])
nrow(seurat.object@meta.data[seurat.object@meta.data$clust.ID == 17,])
nrow(seurat.object@meta.data[seurat.object@meta.data$clust.ID == 3,])
```

>>>>

```{r setup}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/")
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
# library(clustree)
```
store session info
```{r }
# sink("CMP-v1.20210616.txt")
sessionInfo()
# sink()
```

@@

```{r echo = FALSE}
all.genes <- rownames(seurat.object)
seurat.object <- ScaleData(seurat.object, features = all.genes, vars.to.regress = c("nFeature_RNA", "nCount_RNA"))
```

## Save raw object
```{r}
saveRDS(seurat.object, file = paste0(projectName, "_raw.RDS"))
```

@@

```{r}
DimPlot(seurat.object, reduction = "pca", group.by = "orig.ident")
VizDimLoadings(seurat.object, dims = 1:6, nfeatures = 10, reduction = "pca", ncol = 3)

@@

# Add cluster IDs from Seurat v1

do numbers make sense?
```{r}
nrow(seurat.object@meta.data[seurat.object@meta.data$clust.ID == 10,])
nrow(seurat.object@meta.data[seurat.object@meta.data$clust.ID == 11,])
nrow(seurat.object@meta.data[seurat.object@meta.data$clust.ID == 17,])
nrow(seurat.object@meta.data[seurat.object@meta.data$clust.ID == 3,])
```

### Color palette
```{r}
color.palette <- c(
	"coral",
	"chartreuse4",
	"goldenrod1",
	"cadetblue1",
	"burlywood",
	"brown",
	"brown1",
	"blue",
	"blue4",
	"azure3",
	"aquamarine",
	"antiquewhite",
	"cadetblue",
	"gold3",
	"black",
	"darkgreen",
	"deeppink",
	"darkviolet",
	"darkturquoise",
	"darkslategray",
	"darksalmon",
	"darkorchid1",
	"darkolivegreen2",
	"forestgreen",
	"dodgerblue",
	"green",
	"lightpink",
	"lightcoral",
	"khaki1",
	"maroon",
	"peru",
	"lightseagreen",
	"lightsalmon",
	"plum",
	"moccasin",
	"tan",
	"tan1", 
	"red", 
	"purple",
	"khaki4",
	"black", 
	"plum4"
)
```

@@
